---
title: "Data 607 Assignment 2 SQL/R"
author: "Wilson Chau"
date: "2022-12-05"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#Introduction

I created a google survey form and received a few data collected. I transfer the csv file into github and got the data cleaned up and started on this assignment.
```{r}
library(RMySQL)
library("dplyr")
library(tidyverse)
```

#Converting CSV file to R
I exported the CSV data and used MySQLWorkbench. I exported the Data into Github. 

```{r}
mysql <- read.csv("https://raw.githubusercontent.com/AldataSci/Assignment2-607-/main/Homework2%5B607%5D.csv",header=TRUE,sep=",")
head(mysql)
```

#Figuring out the average 
I went through the average ratings and filter out the NULL value and then null values and then I had to make the chr values under Stars into integer values to calculate the average.
```{r}
avg_mov <- mysql %>%
  group_by(movie) %>%
  filter(Stars != "NULL") %>%
  summarise(avg= mean(as.integer(Stars)))
avg_mov
```
Once I cleaned the data I went to visualize it
```{r}
library(ggplot2)
ggplot(data=avg_mov, aes(x=movie,y=avg , fill=movie)) + 
  coord_flip() +
  geom_bar(stat="identity")
```
From this Survey I see Spider-Man No Way Home was the best option to watch.

#Movies not recommended

```{r}
nul <- mysql %>%
  group_by(movie) %>%
  filter(Stars=="NULL") %>%
  count(Stars,sort=TRUE)
nul
library(ggplot2)
ggplot(data=nul,aes(x=movie,y=n,fill=movie)) +
  geom_bar(stat="Identity")
```